Summary Tables

### 2020-02-21 summary_tables_outcomes.Rmd
Update path
Regen
Add injury risks to a csv file

   readr::write_csv(td, paste0('results/multi_city/whw_', cs, '.csv'))

@@

### DT - Who hit whom matrix for all case cities {#whw_all}

#### Baseline

@@

>>>>

   readr::write_csv(td, paste0('results/multi_city/whw_matrices/whw_', cs, '.csv'))

@@

### DT - Who hit whom matrix for all case cities {#whw_all}
Baseline

@@

readr::write_csv(td, 'results/multi_city/whw_matrices/injury_risks.csv')
